Type Safe Redis Queries

### 2017-07-14 TyDe2017/main-tyde.tex
Minor formatting/layout changes.
Public domain issues.

\makeatletter\if@ACM@journal\makeatother
%% Journal information (used by PACMPL format)
%% Supplied to authors by publisher for camera-ready submission
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{1}
\acmArticle{1}
\acmYear{2017}
\copyrightyear{2017}
\acmPrice{15.00}

\setcopyright{rightsretained}
\bibliographystyle{ACM-Reference-Format}

\usepackage{amsmath}
%\usepackage{amsfonts}
%\usepackage{amsthm}
%\usepackage{color}
\usepackage{xcolor}
\usepackage{url}
\usepackage{mathptmx}
\usepackage{doubleequals}
%\usepackage{makeidx}  % allows for indexgeneration
\usepackage{textcomp} % for single quote
\usepackage{fancyvrb} % for indented verbatim

@@

\setlength{\mathindent}{10pt}

@@

\author{Ting--Yan Lai}
\authornote{Ting--Yan Lai was summer intern from
the Institute of Computer Science and Engineering,
National Chiao Tung University, Taiwan,
when part of this work was developed.}
%% \authornote is optional;
\affiliation{
%  \position{Summer Intern}
  \department{Institute of Information Science}
  \institution{Academia Sinica}
  \streetaddress{128, Academia Road, Section 2}
  \city{Nangang, Taipei City}
  \postcode{115}
  \country{Taiwan}
}
\email{banacorn@gmail.com}          %% \email is recommended

@@

\keywords{Haskell, Redis, Type-Level Programming Type Safety, Key-Value Store}

\maketitle

>>>>

%\makeatletter\if@ACM@journal\makeatother
%% Journal information (used by PACMPL format)
%% Supplied to authors by publisher for camera-ready submission
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{1}
\acmArticle{1}
\acmYear{2017}
\copyrightyear{2017}
\acmPrice{15.00}

%%% The following is specific to TyDe'17 and the paper
%%% 'Type Safe Redis Queries: A Case Study of Type-Level Programming in Haskell'
%%% by Ting-Yan Lai, Tyng-Ruey Chuang, and Shin-Cheng Mu.
%%%
\setcopyright{licensedothergov}
\acmDOI{10.1145/3122975.3122978}
\acmISBN{978-1-4503-5183-6/17/09}
\acmConference[TyDe'17]{2st ACM SIGPLAN International Workshop on Type-Driven Development}{September 3, 2017}{Oxford, UK}
\acmYear{2017}
\copyrightyear{2017}
\acmPrice{15.00}

\bibliographystyle{ACM-Reference-Format}

\usepackage{amsmath}
%\usepackage{amsfonts}
%\usepackage{amsthm}
%\usepackage{color}
\usepackage{xcolor}
\usepackage{url}
%\usepackage{mathptmx}
\usepackage{doubleequals}
%\usepackage{makeidx}  % allows for indexgeneration
\usepackage{textcomp} % for single quote
\usepackage{fancyvrb} % for indented verbatim
\usepackage{flushend} % balance columns on last page

@@

\pagestyle{empty} %no page number
\setlength{\mathindent}{10pt}

@@

\author{Ting--Yan Lai}
\authornote{Ting--Yan Lai was a summer intern from
the Inst. of Computer Science and Engineering,
National Chiao Tung Univ., Taiwan,
when part of this work was developed.}
%% \authornote is optional;
\affiliation{
%  \position{Summer Intern}
  \department{Institute of Information Science}
  \institution{Academia Sinica}
  \streetaddress{128, Academia Road, Section 2}
  \city{Nangang, Taipei City}
  \postcode{115}
  \country{Taiwan}
}
\email{banacorn@gmail.com}          %% \email is recommended

@@

\keywords{Haskell, Redis, Type-Level Programming, Type Safety, Key-Value Store}

\maketitle
\thispagestyle{empty}
